\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Angel Velazquez}}\\
	21velazquezang@gmail.com $\cdot$ 442-456-4161 $\cdot$ https://www.linkedin.com/in/angel-velazquez-35998729a/\\
\end{center}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
	 Agile Workflow, Azure AI, C, C++, Confluence, Flutter, Github, Jira, Python, React, RESTful API\textquotesingle{}s, SQL \\
\end{tabular}
\vspace{0mm}

%==== Experience ====%
\header{Technical Experience}
\vspace{1mm}

\textbf{Paychex} \hfill Remote\\
\textit{Software Engineer Intern} \hfill September 2024 - Present 
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and developed an AI-powered chatbot to streamline data navigation for Paychex developers by utilizing React for frontend development and integrating Jira and REST APIs for dynamic data handling with Azure AI Search.
	\item Spearheaded the integration of RESTful APIs with seamless Jira workflows, which automated the team’s ability to access and manage project data effectively.
	\item Guided team members in best practices for React development, API integration, and agile methodologies, ensuring high-quality code and fostering a collaborative and productive work environment.
	\item Collaborated on the architectural design and development of a user-friendly interface.
\end{itemize}
\textbf{California Department of Corrections and Rehabilitation} \hfill Imperial, CA\\
\textit{CDCR IT Assistant} \hfill August 2024 - September 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Increased team productivity by 25\% by deliverering comprehensive IT support for an enterprise team at a CDCR prison, including system configuration, network maintenance, and user support, ensuring seamless daily operations and enhanced system reliability.
	\item Took initiative of system configuration, troubleshooting, and ticket management.
\end{itemize}
\textbf{Imperial Irrigation District} \hfill Imperial, CA\\
\textit{SCADA Engineer Intern} \hfill Summer 2022 - Summer 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Managed multiple project timelines and coordinated between departments to ensure timely updates and upgrades of SCADA components, demonstrating strong organizational and leadership skills.
	\item Provided technical support and conducted training sessions for new interns on SCADA operation and maintenance, improving team skills and knowledge base.
	\item Enhanced substation SCADA system efficiency by 10\% by designing and implementing a sorting algorithm that optimized data input processing, resulting in faster decision-making and system responsiveness.
 %==== \item Created and regularly updated As-Built AutoCAD drawings to reflect current specifications for various SEL devices, including ICON and RTACs, ensuring accuracy and compliance with engineering standards. ====%

	\end{itemize}

%==== Leadership Experience ====%
\header{Leadership Experience}
\vspace{1mm}

\textbf{Chick-fil-A} \hfill Phoenix, AZ\\
\textit{Back-of-house Shift Leader} \hfill October 2023 - May 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Demonstrated exceptional time management, consistently prioritizing tasks to meet tight deadlines and customer load, ensuring continuous product availability.
	\item Took initiative to support team members, assisting with training and providing guidance to ensure all employees were aligned with restaurant goals and operational standards.
	\item Contributed to overall team success, stepping in to fill gaps as needed, whether by getting on fry station, hopping on machines, or handling special customer requests, always with a focus on teamwork.
 
\end{itemize}

%==== Projects ====%
\header{Projects}
{\textbf{Out There Social Club}} {\sl Flutter, WordPress, SQL} \hfill https://github.com/2024-Arizona-Opportunity-Hack/Hackathon-Queens-OutThereSocialClubat-OutThereSocialClub-ASUWebsiteandMembershipSystem\\
Developed a cross-platform mobile application with a team using Flutter for the frontend and WordPress for the backend. The app provided a responsive and user-friendly interface, seamlessly integrating with WordPress for dynamic content management. I worked closely with the chief officers to gather requirements, ensuring the app aligned with business objectives while offering features like user authentication, real-time content updates, and smooth in-app navigation to enhance the overall user experience.\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{Grand Canyon University}\hfill Phoenix, AZ\\
BS Computer Science \hfill Sep 2021 - May 2025\\
\vspace{2mm}


\ 
\end{document}