\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Angel Velazquez}}\\
	21velazquezang@gmail.com $\cdot$ 442-456-4161 $\cdot$ www.linkedin.com/in/angel-vlzqz\\
\end{center}

%==== Skills ====%
\header{Skills}
\begin{tabular}{ l l }
    Real-Time Monitoring, SCADA, Data Analysis, Microsoft Excel,
    Python, SQL, Jira, Agile Workflow, \\ Azure AI, React, RESTful APIs, Flutter, C, C++, GitHub \\
\end{tabular}
\vspace{0mm}

%==== Experience ====%
\header{Technical Experience}
\vspace{1mm}

\textbf{Paychex} \hfill Remote\\
\textit{Software Engineer Intern} \hfill September 2024 - April 2025 
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and developed an AI-powered chatbot to streamline data navigation for Paychex developers by utilizing React for frontend development and integrating Jira and REST APIs for dynamic data handling with Azure AI Search.
	\item Spearheaded the integration of RESTful APIs with seamless Jira workflows, which automated the team’s ability to access and manage project data effectively.
	\item Guided team members in best practices for React development, API integration, and agile methodologies, ensuring high-quality code and fostering a collaborative and productive work environment.
\end{itemize}
\textbf{California Department of Corrections and Rehabilitation} \hfill Imperial, CA\\
\textit{CDCR IT Assistant} \hfill August 2024 - September 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Delivered comprehensive technical support and maintained network systems critical to secure facility operations.
    \item Gained hands-on experience with live monitoring systems, hardware diagnostics, and alert resolution in a fast-paced environment.
    \item Managed and tracked IT tickets with a focus on maintaining uptime and system readiness, aligning with 24/7 operational demands.
\end{itemize}
\textbf{Imperial Irrigation District} \hfill Imperial, CA\\
\textit{SCADA Engineer Intern} \hfill Summer 2022 - Summer 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Monitored and analyzed SCADA system operations in real-time to ensure stability of power delivery across grid assets.
    \item Designed and implemented a sorting algorithm to optimize substation SCADA data input, improving response times by 10\%.
    \item Provided cross-departmental coordination to maintain uptime and performance during SCADA component updates.
    \item Assisted in outage tracking and system data trending, contributing to improved transmission forecasting accuracy.
\end{itemize}
 %==== \item Created and regularly updated As-Built AutoCAD drawings to reflect current specifications for various SEL devices, including ICON and RTACs, ensuring accuracy and compliance with engineering standards. ====%

%==== Leadership Experience ====%
%\header{Leadership Experience}
%\vspace{1mm}

%\textbf{Chick-fil-A} \hfill Phoenix, AZ\\
%\textit{Back-of-house Shift Leader} \hfill October 2023 - May 2024\\
%\vspace{-1mm}
%\begin{itemize} \itemsep 1pt
	%\item Demonstrated exceptional time management, consistently prioritizing tasks to meet tight deadlines and customer load, ensuring continuous product availability.
	%\item Took initiative to support team members, assisting with training and providing guidance to ensure all employees were aligned with restaurant goals and operational standards.
	%\item Contributed to overall team success, stepping in to fill gaps as needed, whether by getting on fry station, hopping on machines, or handling special customer requests, always with a focus on teamwork.
 
%\end{itemize} 

%==== Projects ====%
\header{Projects}
{\textbf{Out There Social Club}} {\sl Flutter, WordPress, SQL} \hfill https://github.com/2024-Arizona-Opportunity-Hack/Hackathon-Queens-OutThereSocialClubat-OutThereSocialClub-ASUWebsiteandMembershipSystem\\
Developed a cross-platform mobile application with a team using Flutter for the frontend and WordPress for the backend. The app provided a responsive and user-friendly interface, seamlessly integrating with WordPress for dynamic content management. I worked closely with the chief officers to gather requirements, ensuring the app aligned with business objectives while offering features like user authentication, real-time content updates, and smooth in-app navigation to enhance the overall user experience.\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{Grand Canyon University}\hfill Phoenix, AZ\\
BS Computer Science \hfill Sep 2021 - May 2025\\
\vspace{2mm}


\ 
\end{document}
